\documentclass{article}

\usepackage{amsmath}

\title{Circuit Design for Security}
\author{Fabian Olbert}
\begin{document}
\maketitle
  
\section{Performance Metrics}

Further Readings: Digital Integrated Circuit Design – From VLSI Architectures to CMOS Fabrication; Cambridge University Press, 2008

\subsection{Hardware Complexity}
For ICs or \textbf{ASICs} the \textit{area} of the logic is generally determined by the area in gate equivalents. 
1GE is typically one NAND gate (2 PMOS + 2NMOS). 
The \textit{memory} is determined by the amount of SRAM, DRAM, ROM...

For \textbf{FPGAs} the \textit{area} is measured in slices. The unit to measure these area is the basic elements (Flip Flops, LUTs, DSP slices etc.)
The \textit{memory} is determined by the amount of distributed RAM (LUTs utilized as RAM) and the Block RAM.

\subsection{Timing Related Performance}
The \textit{Critical Path Dealy} is proportional to the number of gates and the wire length in the longest path from one register to the next. It determines the maximum frequency.

The \textit{Latency} is determined by the number of clock cycles required to perform the operation. There is a trade off between the critical path delay and the latency. 

The \textit{Throughput} is the amount of the processed data per processed time.

Assume there is a critical path with a path delay of 15ns. 

\begin{equation}
  
  f_{max} = \frac{1}{15ns} \approx 66.67MHz
% f_{max} = \frac{1}{15\,\text{ns}} \approx 66.67\,\text{MHz}
\label{eq:freq}
\end{equation}

\section*{Example - Timing Related Performances}

Assume Design with
\begin{itemize}
    \item Latency $L = 1$
    \item Critical Path Delay (assume: incl. setup time, hold time, etc.): $d = \SI{15}{ns}$
    \item $\rightarrow$ Maximum frequency $f \approx \SI{66.67}{MHz}$
    \item $\rightarrow$ Throughput when ```processed data'' = k:
          \[
              throughput = \frac{k}{k \cdot \SI{15}{ns}} \approx 66.6 \cdot 10^6 \, \frac{\text{data}}{\text{s}}
          \]
\end{itemize}

Pipelining (put registers in logic path):
\begin{itemize}
    \item Latency $L = 3$
    \item Critical Path Delay $d = \SI{5}{ns}$
    \item $\rightarrow$ Maximum frequency $f \approx \SI{200}{MHz}$
    \item $\rightarrow$ Throughput when ```processed data'' = k:
          \[
              \lim_{k \to \infty} (throughput) = \lim_{k \to \infty} \frac{k}{k \cdot \SI{5}{ns} + \SI{10}{ns}} = 200 \cdot 10^6 \, \frac{\text{data}}{\text{s}}
          \]
\end{itemize}
\end{document}
